%All Episodes are Regarded with subsection and only referred to with name%
\subsection{First Match}
\begin{itemize}
    \item We are introduced to the Main Character, Zane.
    \item It starts off with a "dream" or "vision", of a talk between Prestige and 
    someone who Zane is seeing perspective of. 
    \item Zane is shown to want to prove himself, and to redeem his father. 
        \begin{itemize}
            \item Shown participating in class, even when he was wrong in most questions. 
        \end{itemize}
    \item Zane is later shown following a classmate to an abandoned classroom, where 
    he sees a table in which it has a symbol similar to a deck he owns. 
    \item Zane meets Lulo, and they have their first match, where Zane learns how to play
        \begin{itemize}
            \item Zane (Warriors - Basics)
            \item Lulo (Mythicals - United)
        \end{itemize}
    \item Zane loses but Lulo seems potential in him
\end{itemize}
%
\subsection{Finn's Fan Fave Shop}
\begin{itemize}
    \item Lulo brings Zane to a Card Shop, Finn's Fan Fave Shop, where Zane can be trained. 
    \item Zane asking the owner, Finn where the owner can be found, is misunderstood as a punk. 
    \item Finn challenges Zane, and Zane blindly accepts. 
        \begin{itemize}
            \item Finn (Titans - )
        \end{itemize}
    \item Zane loses, and Finn is told he is there to train from Lulo, so then Zane is accepted 
    into Finn's training program. 
\end{itemize}

\subsection{}