\documentclass[12pt, letterpaper]{memoir}
\title{Phaktionz-Story}
\author{Mustafif Khan}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
colorlinks=true, % make the links colored
linkcolor=black, % color TOC links in blue
urlcolor=red, % color URLs in red
linktoc=all % 'all' will create links for everything in the TOC
}
\usepackage{dramatist}
\usepackage{calc}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\thetitle}
\rhead{\theauthor}
\rfoot{Page \thepage}
\begin{document}
\maketitle
\pagenumbering{arabic}
\newpage
\tableofcontents
\newpage
%Characters
\Character[Main Character]{Zane}{Zane}
%
\Character[Male Companion]{Lulo}{Lulo}
\Character[Coach/Shop Owner]{Finn}{Finn}
\Character[Friend/"Rival"]{Percy}{Percy}
\Character[Mentee]{Brexton}{Brexton}
%
%Villians 
\Character[Main Antagonist Character]{Zeppelin}{Zeppelin}
\Character[Main Rival Character]{Hayes}{Hayes}
%
\Character[Main Henchman]{Syco}{Syco}
\Character[Former Champion]{Nimu}{Nimu}
%
%Origins
\Character[Prestige, Mage Origin]{Prestige}{Prestige}
%
%Other Extras 
\Character[Any Teacher]{Teacher}{Teacher}
%
\setlength{\speakswidth}{\widthof{\speaksfont Therapist}}
\addtolength{\speakswidth}{\Dlabelsep}
\addtolength{\speaksindent}{\speakswidth}

%Each Arcs will be represented as an act
\act[\\The Origin's Quest]
%Each Episode will be used a scene 
\scene[\textbf{First Game}]
\StageDir{
    \begin{center}
        We start off seeing the war of the Phaktionz’ Realms, Prestige walks in
    \end{center}
}
\begin{drama}
    \Prestigespeaks{My bigotry has blinded me to this chaos, we must hurry, our solution will not be found here!}
\end{drama}
\StageDir{
    \begin{center}
        Zane suddenly wakes up, confused about his dream, but doesn't think much of it. He looks around 
    \end{center}
}
\begin{drama}
    \Zanespeaks{I swear I heard a heard around here somewhere?}
\end{drama}
\StageDir{
    \begin{center}
        Looks at his deck
    \end{center}
}
\begin{drama}
    \Zanespeaks{I can’t get my head scrambled today, I have a mission I need to complete, I need to redeem my father!}
\end{drama}
\StageDir{
    \begin{center}
        Gets out of his bed, feeling a sense of purpose and motivation
        \\\textbf{-T h e m e s o n g -}
        \\Zane is in class, constantly trying to answer the teacher's questions, but is getting every answer wrong, the class laughs except for one student. The teacher approaches Zane after class
    \end{center}
}
\begin{drama}
    \Teacherspeaks{You seemed pretty excited today, Mr. Zane, for better or for worse}
    \Zanespeaks{Yeah, today I have to prove myself, so I thought I’d try in class, well guessing didn’t help out my mark, but it did help me motivate myself, which is just what I need}
    \Teacherspeaks{Well good luck in your proving, next time I hope you're more prepared but the participation was nice, have a  good day Mr. Zane}
\end{drama}
\StageDir{
    \begin{center}
        Zane notices someone was watching him from the door, he starts to chase the stalker. Eventually, he finds himself in an abandoned classroom with a familiar mat lying on a table. 
    \end{center}
}
\begin{drama}
    \Zanespeaks{Wait, that mat has the same symbol as my cards}
\end{drama}
\StageDir{Zane takes out his deck to confirm}
\begin{drama}
    \Lulospeaks{Indeed it does}
\end{drama}
\end{document}